---
title: "Homework 1" 
author: "Zabih Yousuf"
fontsize: 12pt
geometry: margin=1in
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, highlight=FALSE)
```

## Problem 1   
```{r}

```
// 1. This variable does not work because R does not allow a variable to start with a number.

// 2. A period is allowed in the beginning of variables but since the period is followed by a number, it is not allowed. 

// 4. Leading underscores are not allowed in R.

// 6. This variable contains a space which the complier reads as the variable name is now just the number so it will assign the value to simply the number which will result in a crash. 

// 7. Having parenthesis will make R think you are declaring a function and functions cannot be assigned a variable.



## Problem 2
### Part A
```{r}
553.9/51.3
```

### Part B
```{r}
floor(533.9/51.3)
```

### Part C
```{r}
(553.9/679.4)*100

```

### Part D
```{r}
Q2 <- (559.9/608.8)*100
sprintf("Q2 Profit: %s", Q2)
Q3 <- (553.9/679.4)*100
sprintf("Q3 Profit: %s", Q3)

if(Q2 - Q3 != 0){
print ("Yes")
}
```

### Part E
```{r}
Q2 <- (559.9/608.8)*100
Q3 <- (553.9/679.4)*100
Q2-Q3

```

### Part F
```{r}
107.5-51.3

```

## Problem 3
### Part A
```{r}
vecA <- rep("Q1",times=4)
vecA
```

### Part B
```{r}
vecB <- seq(from = 50.0,to = 100.0,by = 2.5)
vecB
```

### Part C
```{r}
vecC <- rep(2010:2017, each=4)
vecC
```

### Part D
```{r}
vecD <- rep(2016:2017, c(4,3))
vecD
```

### Part E
```{r}
vecE <- rep(1295:1300)
vecE2 <- seq(from = 1299, to = 1290, by = -1)
c(vecE,vecE2)
```

### Part F
```{r}
vecF <- seq(from = 4160,to = 3530,by = -105)
vecF
```